Unsupervised embeddings capture latent structure of scientific mobility

### 2020-02-24 paper/current/main.tex
add_clusim_ref_and_add_explnation

%
% Figure - CLUSTERING
%
\begin{figure}[p!]
	\centering
	\label{fig:clustering}
	\includegraphics[width=\textwidth]{\figdir/Clustering/cluster_country.pdf}
	\caption{
		\textbf{Geography, then language, dictate international mobility.}
		\textbf{a.} Hierarchically clsutered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country, excluding the United States. 
		Color of matrix cells corresponds to similarity between country vectors.
		Color of country names corresponds to their cluster.
		Color of three cell rows separated from the matrix correspond to, from left to right, the continent of the country, the language family, and the individual language. 
		\textbf{b.}	\textit{CluSim} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$. 
		Continent better explains the grouping of country vectors at higher levels of the clustering processes.
		Language family, and then majority spoken language, better explain the grouping of countries at more granular 
	}
\end{figure}

>>>>

%
% Figure - CLUSTERING
%
\begin{figure}[p!]
	\centering
	\label{fig:clustering}
	\includegraphics[width=\textwidth]{\figdir/Clustering/cluster_country.pdf}
	\caption{
		\textbf{Geography, then language, dictate international mobility.}
		\textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has a more than 25 organizations, excluding the United States. 
		Color of matrix cells corresponds to similarity between country vectors.
		Color of country names corresponds to their cluster.
		Color of three cell rows separated from the matrix correspond to, from left to right, the continent of the country, the language family, and the individual language. 
		\textbf{b.}	\textit{CluSim} \cite{gates2019element} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$. 
		Continent better explains the grouping of country vectors at higher levels of the clustering processes.
		Language family, and then majority spoken language, better explain the grouping of countries at more granular. 
	}
\end{figure}
